{\fontfamily{ptm}\selectfont My Ideas after Reading Papers}

### 2025-08-03 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

    In this section, we will proposed our ideas which relaxed Necoara's conditions for strong convexity.

@@

    semi Bregman Divergence is the Bregman Divergence of distance squared to a set. 

@@

    \begin{theorem}[Bregman Divergence for distance squared]\label{thm:bd-dist-sq}

@@

@@

    The abbreviation ``SBD'' stands for ``Semi Bregman Divergence''. 

@@

    \begin{lemma}[conditions when SBD behaves like SCNVX]

@@

        Define the set $\mathcal D(x | C) := \{z \in \RR^n : \Pi_C z = \Pi_C x\}$. 

@@

            (\forall z \in D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 

@@

    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so we have

@@

    \begin{assumption}[our assumptions]\label{ass:our-ass}
        The following assumption is about $(f, g, L_f, X^*)$. 
        \begin{enumerate}
            \item $f: \RR^n \rightarrow \RR$ is $L_f$ Lipschitz smooth. 
            \item $g: \RR^n \rightarrow \RR$ is l.s.c
            \item Denote $X^*$ be the fixed point set of $T_{L_f, f, g}$ and assume $X^* \neq \emptyset$. 
        \end{enumerate}
    \end{assumption}
    \begin{definition}[relatively quasi strongly convex]
        Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
        The function $F = f + g$ is relatively quasi strongly convex if there exists $\kappa_f > 0$ such that for all $x \in \dom g$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
        \begin{align*}
            \left(\forall v \in \partial F(\bar x)\right)\;
            F(x) - F(\bar x) - \langle v, x - \bar x\rangle 
            &\ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2. 
        \end{align*}
    \end{definition}
    \begin{remark}
        Take note that the RHS of the inequality $\kappa_f/2 \Vert x - \bar x\Vert^2 = D_\varphi(x, \Pi_{X^*}x)$ where $\varphi = (1/2)\dist(x | X^*)^2$. 
    \end{remark}
    The following discussion will give important consequences of our set up. 
    % ------------------------------------------------------------------------------------------------------------------
    \subsection{examples for relatively quasi strongly convex functions}

    % ------------------------------------------------------------------------------------------------------------------
    \subsection{theorems useful for convergence analysis of algorithms}

>>>>

    In this section, we will propose our ideas which relaxed Necoara's conditions for strong convexity.

@@

@@

    \begin{theorem}[distance squared Bregman Divergence]\label{thm:bd-dist-sq}

@@

    In the parts that come, we will talk about the set of points that share the same projections onto a set.
    Let $C \subseteq \RR^n$, we define for all $x \in \RR^n$ the set: 
        \mathcal D(x | C) = \{z \in \RR^n : \Pi_C z = \Pi_C x\}. 

@@

    The abbreviation ``DSBD'' stands for ``distance squared Bregman Divergence''. 

@@

    \begin{lemma}[conditions when DSBD behaves like norm squared]

@@

@@

            (\forall z \in \mathcal D(x | C))\; \mathcal D_\varphi(x, z) = \frac{1}{2}\Vert x - z\Vert^2 = D_f(z, x). 

@@

    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so, we have

@@

    The following assumption is the weakest and, it doesn't assume convexity at all. 
    \begin{assumption}[our assumptions]\label{ass:our-ass}
        The following assumption is about $(f, g, L_f, X^*)$. 
            \item $f: \RR^n \rightarrow \RR$ is $L_f$ Lipschitz smooth. 
            \item $g: \RR^n \rightarrow \RR$ is l.s.c
            \item Denote $X^*$ be the fixed point set of $T_{L_f, f, g}$ and assume $X^* \neq \emptyset$. 
    \end{assumption}
    \begin{definition}[restricted QUA]
        Suppose that $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
        The function $F = f + g$ has restricted QUA condition if there exists $\kappa_f > 0, D \subseteq \dom g$ such that for all $x \in D$, let $\bar x = \Pi_{X^*}x$ it satisfies: 
            \left(\forall v \in \partial F(\bar x)\right)\;
            F(x) - F(\bar x) - \langle v, x - \bar x\rangle 
            &\ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2. 
        Take note that the RHS of the inequality $\kappa_f/2 \Vert x - \bar x\Vert^2 = D_\varphi(x, \Pi_{X^*}x)$ where $\varphi = (1/2)\dist(x | X^*)^2$. 
        This definition doesn't exclude nonconvex functions. 
        The hope is to have the set $D = \dom g$, but we don't think that is always true. 
        Our hope is that the set $D$ is at least somewhat larger than $X^+$. 
    The following discussion will give important consequences of this setup. 
    \subsection{examples for relatively quasi strongly convex functions}
        The following assumption will characterize a specific type of convex programming problem that has relative quasi strong convexity. 
        \begin{assumption}[distance of two sets]
            Suppose $(f, g, L_f, X^*)$ satisfies Assumption \ref{ass:our-ass}. 
            In addition, we assume the following. 
            \begin{enumerate}[nosep]
                \item 
        \end{assumption}
        \begin{theorem}[example of restricted QUA]\label{thm:example-rqua}

        \end{theorem}
        \begin{proof}

        \end{proof}
    % ------------------------------------------------------------------------------------------------------------------
    \subsection{theorems useful for convergence analysis of algorithms}
        The proximal gradient inequality and, the Jensen inequality are the most important for deriving convergence rate of first order accelerated method.
